The Impact of Malaria Episodes and Treatment Regimens on Adverse Pregnancy Outcomes in Ugandan Women

### 2025-03-30 products/manuscript/Manuscript.qmd
Update1

**Figure 1: Distribution of Total Malaria Episodes**
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
# Load required packages
library(ggplot2)

# Create a histogram of total malaria episodes
ggplot(data = promo_data_clean, aes(x = total_malaria_episodes)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black") +
  labs(
    title =,
    x = "Total Malaria Episodes",
    y = "Count"
  )
```

@@

*Table 2: Association Between Malaria Episodes and Risk of Preterm Birth*
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Create cleaned table for Table 2
table_preterm_pars_clean <- tribble(
  ~Variable, ~`Adjusted Odds Ratio (aOR)`, ~`95% CI Lower`, ~`95% CI Upper`, ~`p-value`,
  "Total malaria episodes during pregnancy", 1.04, 0.95, 1.14, 0.401,
  "Age at enrollment (years)", 0.99, 0.96, 1.03, 0.697,
  "Gravidity", 0.91, 0.82, 1.02, 0.106,
  "Parity", 1.17, 1.05, 1.30, 0.005,
  "Hypertension", 0.89, 0.65, 1.22, 0.463,
  "Diabetes mellitus", 1.22, 0.88, 1.69, 0.237
)

# Display table with consistent styling
kable(table_preterm_pars_clean,
      caption = "",
      col.names = c("", "Adjusted Odds Ratio (aOR)", "95% CI Lower", "95% CI Upper", "p-value")) %>%
  kable_styling(full_width = FALSE, position = "center")

@@

*Table 3: Association Between Malaria Episodes and Risk of Stillbirth*
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
library(logistf)

# Run parsimonious stillbirth model
model_stillbirth_pars <- logistf(
  stillbirth_bin ~ total_malaria_episodes_during_pregnancy +
    age_at_enrollment_years + gravidity + parity +
    hypertension + diabetes_mellitus,
  data = promo_data_clean
)

@@

# Replace raw names with neat labels; replace any NA (i.e., unmapped) with blank
table_stillbirth_pars$Variable <- variable_labels[table_stillbirth_pars$Variable]
table_stillbirth_pars$Variable[is.na(table_stillbirth_pars$Variable)] <- ""

@@

# Display table with consistent styling and without row names
kable(table_stillbirth_pars,
      row.names = FALSE,
      caption = "*Table 3: Stillbirth Model*",
      col.names = c("Exposure and Adjustment Variables", "Adjusted Odds Ratio (aOR)", "95% CI Lower", "95% CI Upper", "p-value")) %>%
  kable_styling(full_width = FALSE, position = "center")

>>>>

**Figure 1: Distribution of Total Malaria Episodes**
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
# Create a histogram of total malaria episodes
ggplot(data = promo_data_clean, aes(x = total_malaria_episodes)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black") +
  labs(
    title =,
    x = "Total Malaria Episodes",
    y = "Count"
  )
```

@@

*Table 2: Association Between Malaria Episodes and Risk of Preterm Birth*
```{r, echo=FALSE, message=FALSE, warning=FALSE}

table_preterm_pars_clean <- tribble(
  ~Variable, ~`Adjusted Odds Ratio (aOR)`, ~`95% CI Lower`, ~`95% CI Upper`, ~`p-value`,
  "Total malaria episodes during pregnancy", 1.04, 0.95, 1.14, 0.401,
  "Age at enrollment (years)", 0.99, 0.96, 1.03, 0.697,
  "Gravidity", 0.91, 0.82, 1.02, 0.106,
  "Parity", 1.17, 1.05, 1.30, 0.005,
  "Hypertension", 0.89, 0.65, 1.22, 0.463,
  "Diabetes mellitus", 1.22, 0.88, 1.69, 0.237
)

# Display table with consistent styling
kable(
  table_preterm_pars_clean,
  format = "pandoc",
  caption = "*Table 2: Association Between Malaria Episodes and Risk of Preterm Birth*",
  col.names = c("Exposure and Adjustment Variables", "Adjusted Odds Ratio (aOR)", "95% CI Lower", "95% CI Upper", "p-value")
) %>%
  kable_styling(full_width = FALSE, position = "center")

@@

*Table 3: Association Between Malaria Episodes and Risk of Stillbirth*
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
# Run parsimonious stillbirth model
model_stillbirth_pars <- logistf(
  stillbirth_bin ~ total_malaria_episodes_during_pregnancy +
    age_at_enrollment_years + gravidity + parity +
    hypertension + diabetes_mellitus,
  data = promo_data_clean
)

@@

# Replace raw names with neat labels; replace any NA with blank
table_stillbirth_pars$Variable <- variable_labels[table_stillbirth_pars$Variable]
table_stillbirth_pars$Variable[is.na(table_stillbirth_pars$Variable)] <- ""

@@

# Display table with consistent styling using kable with format "pandoc"
kable(
  table_stillbirth_pars,
  format = "pandoc",
  caption = "*Table 3: Association Between Malaria Episodes and Risk of Stillbirth*",
  col.names = c("Exposure and Adjustment Variables", "Adjusted Odds Ratio (aOR)", "95% CI Lower", "95% CI Upper", "p-value")
) %>%
  kable_styling(full_width = FALSE, position = "center")
